---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here: Nicolas Ambrosis

## Exercise 1

Explain what you are visualizing here: SCATTER PLOT. Change in ideology (the higher, the more conservative) in the last 50 years showing different colors for men and women

Put your figure here:

```{r exercise1,echo=FALSE}

####PUT YOUR CODE HERE

cel$female <- recode(cel$female, `1` = "Female", `0` = "Male")

ggplot(data = cel) +
  aes(x = year, y  = dwnom1, color = factor(female)) +
  scale_color_manual(values = c("#d94a98", "#1916ab")) +
  geom_jitter() +
  labs(
    x = "Year",
    y = "Ideology",
    title = "Congress Ideology over the las 50 years",
    color = "Gender"
  )


```

## Exercise 2

Explain what you are visualizing here: Blox Plot: In this graphic you can see the mean Ideology grouped by states for 16 States.

Put your figure here:

```{r exercise2,echo=FALSE}

####PUT YOUR CODE HERE
library(ggthemes)  

cel %>%
  filter(st_name %in% c("AL", "GA", "MA", "MO", "MS", "IN", "LA", "KY",
                         "MI", "VA", "MD", "OK", "NH", "ME", "AZ", "CT")) %>% 
  ggplot() +
  aes(x = st_name, y = dwnom1) +
  geom_boxplot() +
  theme_economist() +
  labs(
    x = "States",
    y = "Ideology",
    title = "Idology by States"
  )

```

## Exercise 3

Explain what you are visualizing here: Line Plot: this plot represente the changing in apples price over the year (fake data)

Put your figure here:

```{r exercise3,echo=FALSE}

####PUT YOUR CODE HERE
library(ggtext)
library(ggthemes)
#create a sequence of years


years <- seq(from=1980,to=2020,by=1)

#fake data for vegetables price

#apple_price <- rnorm(n = 41,mean=15,sd=5)
apple_price <- c(6.327226, 12.002752, 12.593287,  8.412929, 18.718086, 19.146518,
        21.550578, 13.878460, 18.518919,  6.987423, 12.571924, 16.479301,
        9.456109, 16.155841, 11.233189, 21.414669, 10.051653, 17.237984,
        16.853089, 12.779497, 15.051130, 15.676054, 20.425105, 16.775450,
        11.031084, 21.229392, 25.022452,  7.103986, 28.394870, 15.999448,
        8.037262, 19.966910, 19.253743, 12.372442, 16.380708, 17.205219,
        19.864272, 10.112350, 22.141554, 13.033585, 17.392816)



fig_data <- tibble("year"=years,
                   "apple"= apple_price)
                   
ggplot(fig_data) +
  aes(x=years,y = apple) +
  geom_line() +
  labs(
    x = "Years",
    y = "Price",
    title = "Changing of apples price over the years"
  ) +
  theme_fivethirtyeight() +
  annotate("text", x = 2014, y = 28,
           label = "Highest historical price", color = "red", )


```

## Exercise 4

Explain what you are visualizing here: Box Plot showing the number of people that is investor or not and grouped by politic Ideology.

Put your figure here:

```{r exercise4,echo=FALSE}

####PUT YOUR CODE HERE

cces$pid7 <- recode(cces$pid7, `1` = 'Strong Dem',
                    `2` = 'Not Strong Dem.',
                    `3`= "Lean Dem.",
                    `4` = "Independent",
                    `5` =  "Lean Rep.",
                    `6`= "Not Strong Rep.",
                    `7`= "Strong Rep.")

cces$investor  <-  recode(cces$investor, `1` = "YES", `2` = "NO")

ggplot(data = cces) +
  aes(x = factor(investor), fill = factor(investor)) +
  geom_bar() +
  labs(
    x = "Investor",
    y = "Count",
    title = "Number of investors",
    fill = NULL
  ) +
  scale_fill_manual(values = c("black", "red")) +
  facet_grid(~pid7)



```
