---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here:



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
####PUT YOUR CODE HERE
cces$ideo5 <- recode(cces$ideo5, `1`='Conservative', `2` = 'Liberal', `3` = 'Moderate', `4` = 'Very Conservative', `5` = 'Very Liberal')


ggplot(data = cces) +
  aes(x = ideo5, fill = ideo5) +
  geom_bar() +
  xlab("Ideology") + 
  ylab("Count") +
  ggtitle("Respondent Ideology") +
  guides(fill = 'none')

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
####PUT YOUR CODE HERE

cces$pew_religimp <- recode(cces$pew_religimp, `1` = 'Not imp.',
                            `2` = 'Not too imp.',
                            `3` = 'Somewhat imp.',
                            `4` = 'Very imp.')

ggplot(data = cces) +
  aes(x = pew_religimp, fill = ideo5) +
  geom_bar() +
  xlab('Importance of Religion') +
  ylab('Count') +
  ggtitle("Importance of Religion by Ideology")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
####PUT YOUR CODE HERE

semester <-seq(from = 1, to = 6, by =1) 

semester <- c(rep(semester,3))



amanda <- "Amanda"
betty <- "Betty"
carol <- "carol"

student <-c(rep(amanda,6), rep(betty,6), rep(carol,6)) 

grades <- runif(min = 80, max = 100, n = 18)

data = tibble(semester, student, grades)

ggplot(data = data) +
  aes(x = semester, y = grades, color = student) +
  geom_line() +
  facet_wrap(~student) +
  guides(color = 'none') +
  xlab("Semester") +
  ylab("Grade") +
  ggtitle("Students Grades by Semester")
```
